Enriching Object Detection with 2D-3D Registration\\and Continuous Viewpoint Estimation

### 2015-03-28 approach.tex
approach change

To handle intraclass variability, we used various CAD models (sedan, truck, racing car, hatchback etc) to cover intraclass variability and made renderings of these CAD models for various viewpoints. The
CAD models were cached so that when we fine-tune 2D-3D matching, we can render the model instantaneously.
Our renderer can continuously vary yaw, pitch, roll and the focal length as well so that the final fine tuning stage produces accurate the continuous viewpoint, a focal length and a bounding box.

@@

\subsection{Whitened Histograms of Orientations (WHO)}
\label{sec:who}
Our technique for rendering and generating exemplar template detectors on-the-fly
is drawing from recent work. Hariharan \etal. introduced Whitened Histograms of Orientations (WHO)
\cite{Hariharan12}, which uses feature statistics from natural images to whiten HOG
templates, making them more discriminative. Whitening is a common signal
processing operation for decorrelating a set of random variables
\cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
$k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
whitening the signal,

\begin{equation}
\tilde{X}=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening},
\end{equation}

we remove 2nd order correlation between all features. Since collecting covariance
matrix for every template shape is expensive, \cite{Hariharan12} proposed an easy
way to synthesize
covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
method to generate $\Sigma$.

@@

% Since collecting covariance matrix for every template shape
%  is expensive, \cite{Hariharan12} proposed easy way to synthesize
% covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
% method to generate $\Sigma$.

@@

% In \cite{Hariharan12}, the authors compute the mean and covariance matrix by assuming Wide-Sense Stationarity (WSS) of HOG features
% generated from natural images. That is, they assume the mean of a HOG cell is
% independent of its place in the image, and the autocovariance of cells depends
% only on their relative location.

@@

NZ-WHO removes these artifacts so that the background has no effect on the
template response. Let a vectorized HOG features of a rendering image $x\in
\mathcal{R}^{nd}$ be $x=T_f(I_r)$ where $n$ is the number HOG cells and $d$ be
the dimension of HOG feature. We create a new vector $x'$ which contains only
the non-zero elements of $x$. To be specific, let $I_d\in \mathcal{R}^{d\times
    d}$ be the identity matrix, $n'$ be the number of non-zero HOG cells, and a
matrix $S\in \mathcal{R}^{n'd \times nd}$ be the masking matrix that selects
non-zero HOG cell. For instance, a template has  $n=3, n'=2$, and only the
second HOG cell has $0$ norm, then

@@

Then, we can define $x' = S x, \mu' = S\mu, \Sigma' = S \Sigma S^T$.
After solving the resulting system (which is now smaller than
in the WHO approach) we find

>>>>

To handle intraclass variability, we used various CAD models (sedan, truck,
racing car, hatchback etc) to cover intraclass variability and made renderings
of these CAD models from various viewpoints. The CAD models were cached so that
when we fine-tune 2D-3D matching, we can render the model instantaneously. Our
renderer can continuously vary yaw, pitch, roll and the focal length as well so
that the final fine tuning stage produces accurate the continuous viewpoint, a
focal length and a bounding box.

@@

\subsection{Whitened Histograms of Orientations (WHO)}
\label{sec:who}
Our technique for rendering and generating exemplar template detectors
on-the-fly is drawing from recent work. Hariharan \etal. introduced Whitened
Histograms of Orientations (WHO), which uses feature statistics from natural
images to create a large number of classifiers analytically using Linear
Discriminant Analysis(LDA) rather than training SVM
classifiers\cite{Hariharan12}. The confidence score for data $x_i$ can be defined as

\begin{align}
    S(x_i) = w_{x_t}^T x_i
\end{align}

where $w_{x_t} = \Sigma^{-1} (x_t - \mu)$ is a LDA classifier for a template $x_t$.

% \begin{align}
%     S(x_i) = w_{x_t}^T x_i\\
%     w_{x_t} = \Sigma^{-1} (x_t - \mu)
% \end{align}

% The advantage of the approach is twofold: (a) you do not need a large number of
% training and hard negative mining \cite{Felzenszwalb10} (b) it takes a fraction
% of time generate (train) a discriminative template.

% templates, making them more discriminative. Whitening is a common signal
% processing operation for decorrelating a set of random variables
% \cite{Martinsson05, Belouchrani00}. More formally, suppose that we have a
% $k$-dimensional random variable $X \in \mathcal{R}^k$ with $Cov(X)=\Sigma$. By
% whitening the signal,
% 
% \begin{equation}
% \Phi(X)=\Sigma^{-\frac{1}{2}}(X - E[X]) \label{eq:whitening}
% \end{equation}
% 
% we remove 2nd order correlation between all features. Since collecting covariance
% matrix for every template shape is expensive, \cite{Hariharan12} proposed an easy
% way to synthesize
% covariance $\Sigma$ from autocovariance $\Gamma$ and we followed their
% method to generate $\Sigma$.

@@

Since collecting second order statistics to generate a covariance matrix for
every template shape is expensive, \cite{Hariharan12} proposed easy way to
synthesize covariance $\Sigma$. The method \cite{Hariharan12} assumes
Wide-Sense Stationarity(WSS) of HOG features generated from natural images.
Assumption they made was that the mean $\mu$ and autocovariance $\Gamma$ of HOG
features do not vary with respect to the location. In this paper, we followed
their method to generate $\Sigma$.

% is independent of its place in the image, and the autocovariance of cells
% depends only on their relative location.

@@

@@

NZ-WHO removes these artifacts so that the background has no effect on the
template response. Let a vectorized HOG features of a rendering image $x = [ \begin{array}{ccccc}x_1^T & x_2^T & \cdots & x_n^T\end{array} ]^T \in
\mathcal{R}^{nd}$ where $x_i$ is the $i$th HOG cell feature and $n$ is the number HOG cells and $d$ is
the dimension of HOG feature. We create a new vector $x'$ which contains only
the non-zero HOG cell features of $x$. To be specific, let $I_d\in \mathcal{R}^{d\times
    d}$ be the identity matrix, $n'$ be the number of non-zero HOG cells, and a
matrix $S\in \mathcal{R}^{n'd \times nd}$ be the masking matrix that selects
non-zero HOG cells. For instance, a template has  $n=3, n'=2$, and only the
second HOG cell has $0$ norm, then

@@

The matrix selects HOG features that corresponds to the first cell and the third cell. Using the selector $S$, we can define new vectorized HOG features $x' = S x, \mu' = S\mu, \Sigma' = S \Sigma S^T$.
After solving the resulting system (which is now smaller than
in the WHO approach) we find
